Vagueness, Noise, and Signaling

### 2015-01-16 paper/version_02/paper.tex
answer to reviewer comments

A sim-max game consists of a set of states $\States$, a set of
messages $\Messgs$ with much fever messages than states, a prior
probability distribution $\Pr \in \Delta(\States)$ that gives the
occurrence probabilities of states, a similarity metric on states
$\similarity \mycolon \States \times \States \rightarrow \mathds{R}$,
and a utility function $\Utils \mycolon \States \times \States
\rightarrow \mathds{R}$. We identify the receiver's acts with the
states of the world, so that the game is one of guessing the actual
state, so to speak. We also assume that sender's and receiver's
interests are alike, so we only have one utility function. We do not
consider message costs, so utilities only depend on the actual state
and the receiver's response. The utility function should be a
monotonically decreasing function of similarity.

@@

As expected, increasing imprecision leads to higher entropy and lower
expected utility. Importantly, however, imprecision does not
necessarily lead to disastrous decline of communicative success. On
the other hand, imprecision increased the number of outcomes with
convex sender strategies, and led to higher proportions of
convergence. In fact, sufficient impairment always assured convergence
and convexity. It appears that perceptual imprecision leads to
slightly less communicative efficiency, more vagueness but more
regular, well-behaved languages in shorter time.

>>>>

A sim-max game consists of a set of states $\States$, a set of
messages $\Messgs$ with much fewer messages than states, a prior
probability distribution $\Pr \in \Delta(\States)$ that gives the
occurrence probabilities of states, a similarity metric on states
$\similarity \mycolon \States \times \States \rightarrow \mathds{R}$,
and a utility function $\Utils \mycolon \States \times \States
\rightarrow \mathds{R}$. We identify the receiver's acts with the
states of the world, so that the game is one of guessing the actual
state, so to speak. We also assume that sender's and receiver's
interests are alike, so we only have one utility function. We do not
consider message costs, so utilities only depend on the actual state
and the receiver's response. The utility function should be a
monotonically decreasing function of similarity.

@@

As expected, increasing imprecision leads to higher entropy and lower
expected utility. Importantly, however, imprecision does not
necessarily lead to disastrous decline of communicative success. On
the other hand, imprecision increased the number of outcomes with
convex sender strategies, and led to higher proportions of
convergence. In fact, sufficient impairment always ensured convergence
and convexity. It appears that perceptual imprecision leads to
slightly less communicative efficiency, more vagueness but more
regular, well-behaved languages in shorter time.
